Errata

### 2025-04-05 tex/Manuscript-3.tex
Update manuscript title and author list in Manuscript-3.tex; change bibliography style to natbib

\begin{center}
    \textbf{\Large Manuscript 2}

@@

    Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Corinna Gall\textsuperscript{1}, Victoria Rodríguez\textsuperscript{2}, Kristina Witzgall\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4,5}, Rómulo Oses\textsuperscript{6}, Oscar Seguel\textsuperscript{7}, Dirk Wagner\textsuperscript{2,8}, and Thomas Scholten\textsuperscript{1}

@@

\bibliographystyle{apalike}
\bibliography{literatur-M3}

>>>>

\begin{center}
    \textbf{\Large Manuscript 3}

@@

@@

\bibliographystyle{natbib}
\bibliography{literatur-M3}
